---
title: "Rating and waiting by coup-related and control measures"
output: 
  ioslides_presentation:
    smaller: true
date: "2024-02-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
# Load libraries
library(data.table)
setDTthreads(11)
library(ggplot2)
library(stringr)
library(cowplot)
library(testit)
theme_set(theme_minimal()  +
            theme_cowplot(14, font_family = "Helvetica", rel_small = 0.8) + 
            theme(legend.position = "none",
                  strip.text = element_text(size = 9),
                  plot.margin = margin(1.5,2,1.5,2)))
library(brms)
library(gsubfn)
library(plotly)
source("utils.R")
source("ID_measures_func.R")


savedModelsDir <- file.path("..", "saved_models")
cacheDir <- file.path("..", "saved_models", "ID_measures")
res <- 100 # Plotting resolution for lines
n_draws <- 300 # Subset of draws for prediction
rating_model <- "rmm1"

# Colors, lines labels
block_colors <- c("#cc1337", "#005b8d")
block_labels <- c("Coup-related", "General")
block_levels <- c("coup", "general")
block_lines <- c("solid", "dashed")

rmm1 <- brm(file = file.path(savedModelsDir, rating_model))

sampleName <- "v1.01"
source("load_data_and_exclude.R")
list[wait, rating_clps, know_test,
     prob_judge, quest, quality] = load_exclude(sampleName)

quest_text <- unique(wait[, .(questionId, question)])
quest_text[, question := trimws(question)]
quest_text <- unique(quest_text[, .(questionId, question)])
quest_text[, question := gsub('""""', '"', question)]

set.seed(0)
```

```{r ID_rating_plotting, message=FALSE, warning=FALSE, include=FALSE}
# Make plots
list[p_coup_rel_useful, 
     p_coup_rel_confidence, 
     p_coup_rel_affect] <- plot_rating_ID(rmm1, "coup_relevance_s", 
                                          "Coup relevance (std.)")
list[p_coup_att_useful, 
     p_coup_att_confidence, 
     p_coup_att_affect] <- plot_rating_ID(rmm1, "coup_attitude_s", 
                                          "Coup attitude (std.)")

list[p_aff_useful, 
     p_aff_confidence, 
     p_aff_affect] <- plot_rating_ID(rmm1, "affect_s", "Mood (std.)")

list[p_mot_useful, 
     p_mot_confidence, 
     p_mot_affect] <- plot_rating_ID(rmm1, "motivation_s", 
                                          "Motivational activation\n(std.)")

# Set common y limits
list[p_coup_rel_useful,
     p_coup_att_useful,
     p_aff_useful,
     p_mot_useful] <-
  set_common_y_limits(p_coup_rel_useful,
                      p_coup_att_useful,
                      p_aff_useful,
                      p_mot_useful)

list[p_coup_rel_confidence,
     p_coup_att_confidence,
     p_aff_confidence,
     p_mot_confidence] <-
  set_common_y_limits(p_coup_rel_confidence,
                      p_coup_att_confidence,
                      p_aff_confidence,
                      p_mot_confidence)

list[p_coup_rel_affect,
     p_coup_att_affect,
     p_aff_affect,
     p_mot_affect] <-
  set_common_y_limits(p_coup_rel_affect,
                      p_coup_att_affect,
                      p_aff_affect,
                      p_mot_affect)
```

## Model
The first part of this presentation contains plots with the outcome of a model predicting the three question rating measures. It uses a multivariate ordinal regression model. This is the formula for the model:


mv(useful, confidence, affect) ~ `r as.character(rmm1$formula[[1]]$confidence[[1]])[[3]]`

## Average ratings by coup relevance
```{r coup_relevance}
plot_rating_grid(p_coup_rel_useful,
                 p_coup_rel_confidence,
                 p_coup_rel_affect)
```

Lines are predictions from model, points denote raw means+-SE.

## Average ratings by coup attitude
```{r coup_attitude}
plot_rating_grid(p_coup_att_useful, 
     p_coup_att_confidence, 
     p_coup_att_affect
)
```

Lines are predictions from model, points denote raw means+-SE.
Seems like the polynomial does a decent job of capturing the shape here.


## Average ratings by mood
(STAI + Gallup wellbeing)

```{r affect}
plot_rating_grid(p_aff_useful,
                 p_aff_confidence,
                 p_aff_affect)
```

Lines are predictions from model, points denote raw means+-SE.


## Average ratings by motivaitonal activation
(Apathy questionnaire + Regulatory Mode)

```{r motivation}
plot_rating_grid(p_mot_useful,
                 p_mot_confidence,
                 p_mot_affect)
```

Lines are predictions from model, points denote raw means+-SE.

## Coup attitude changes the content deemed useful

```{r use_coup_rel_by_q}
plot_rating_ID_by_q(rmm1,
                    "coup_attitude_s",
                    "Coup attitude (std.)",
                    "useful",
                    "Expected usefulness")
```

Each line is a question. Hover over the line to read the question text.

## Another way of illustrating the same point
```{r use_coup_rel_by_q_heatmap}
plot_rating_ID_by_q(rmm1,
                    "coup_attitude_s",
                    "Coup attitude (std.)",
                    "useful",
                    "Expected usefulness",
                    type = "heatmap")

```

This might be better for a non-interactive plot? The point of the plot is that Coup Attitude changes the content of information deemed useful. This is the directing effect of motivation in fine scale.


## Confidence about the different answers changes with coup attitude

```{r conf_coup_rel_by_q}
plot_rating_ID_by_q(rmm1,
                    "coup_attitude_s",
                    "Coup attitude (std.)",
                    "confidence",
                    "Confidence")
```

Each line is a question. Hover over the line to read the question text.

## Coup attitude changes the expected affective response to each answer

```{r aff_coup_rel_by_q}
plot_rating_ID_by_q(rmm1,
                    "coup_attitude_s",
                    "Coup attitude (std.)",
                    "affect",
                    "Expected affect")
```

Each line is a question. Hover over the line to read the question text.

```{r plot_choice_effects, message=FALSE, warning=FALSE, include=FALSE}
rm(rmm1)
chmq1 <- brm(file = file.path(savedModelsDir, "chmq1"))

# Make predictions and create plots
list[p_rel_wait, p_rel_know] <- plot_choice_ID(chmq1,
                                               "coup_relevance_s",
                                               "Coup relevance")

list[p_att_wait, p_att_know] <- plot_choice_ID(chmq1,
                                               "coup_attitude_s",
                                               "Coup attitude")

list[p_aff_wait, p_aff_know] <- plot_choice_ID(chmq1,
                                               "affect_s",
                                               "Mood")

list[p_mot_wait, p_mot_know] <- plot_choice_ID(chmq1,
                                               "motivation_s",
                                               "Motivation")

# Set common y limits across same response
# list[p_rel_wait,
#      p_att_wait,
#      p_aff_wait,
#      p_mot_wait] <-
#   set_common_y_limits(p_rel_wait,
#                       p_att_wait,
#                       p_aff_wait,
#                       p_mot_wait)
# 
# list[p_rel_know,
#      p_att_know,
#      p_aff_know,
#      p_mot_know] <-
#   set_common_y_limits(p_rel_know,
#                       p_att_know,
#                       p_aff_know,
#                       p_mot_know)

```

## Effects of coup relevance on Choice
```{r choice_coup_relevance}
plot_rating_grid(p_rel_wait, p_rel_know)
```

## Effects of coup attitude on Choice
```{r choice_coup_attitude}
plot_rating_grid(p_att_wait, p_att_know)
```

## Effects of mood on Choice
```{r choice_mood}
plot_rating_grid(p_aff_wait, p_aff_know)
```

## Effects of motivation on Choice
```{r choice_motivation}
plot_rating_grid(p_mot_wait, p_mot_know)
```