---
title: "Rating and waiting by coup-related and control measures"
output: 
  ioslides_presentation:
    smaller: true
date: "2024-02-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
# Load libraries
library(data.table)
setDTthreads(11)
library(ggplot2)
library(stringr)
library(cowplot)
library(testit)
theme_set(theme_minimal()  +
            theme_cowplot(14, font_family = "Helvetica", rel_small = 0.8) + 
            theme(legend.position = "none",
                  strip.text = element_text(size = 9),
                  plot.margin = margin(1.5,2,1.5,2)))
library(brms)
library(gsubfn)
library(plotly)
source("utils.R")


savedModelsDir <- file.path("..", "saved_models")
cacheDir <- file.path("..", "saved_models", "ID_measures")
res <- 100 # Plotting resolution for lines
n_draws <- 300 # Subset of draws for prediction
rating_model <- "rmm1"

# Colors, lines labels
block_colors <- c("#cc1337", "#005b8d")
block_labels <- c("Coup-related", "General")
block_levels <- c("coup", "general")
block_lines <- c("solid", "dashed")

sum_ordinal <- function(pred) {
  pred_mult <- apply(pred, c(1, 2), function(x) sum((1:5) * x))
  pred_sum <- sum_draws(pred_mult)
}

plot_rating_ID <- function(model,
                           col,
                           label,
                           measures = c("coup_relevance_s",
                                        "coup_attitude_s",
                                        "affect_s",
                                        "motivation_s"),
                           quadratic = c("coup_attitude_s"),
                           nbins = 8) {
  # Prepare values for group mean prediction ----
  plot_dat_line <- rbindlist(lapply(unique(model$data$block),
                                    function(x)
                                      data.table(col = plot_seq(model$data[col][model$data$block == x,]),
                                                 block = x)))
  
  colnames(plot_dat_line) <- c(col, "block")
  
  # Set all additional predictors to median
  other_measures <- measures[measures != col]
  plot_dat_line[, (other_measures) := lapply(other_measures, function(x)
    median(model$data[x][[1]]))]
  
  # Compute quadratics
  if (!is.null(quadratic)) {
    lapply(quadratic, function(x) {
      plot_dat_line[, paste0("I(", x, ")^2") := .(get(x) ^ 2)]
    })
  }
  
  plot_pred <- function(resp,
                        resp_label) {
    print(paste0("Plotting ", resp_label, " by ", label))
    # Predict for group mean ----
    # Predict - this returns ndraws x npoints x 5
    print("Predicting population effect")
    pred_line <- fitted(
      model,
      newdata = plot_dat_line,
      re_formula = NA,
      summary = F,
      resp = resp
    )
    
    # Summarize into mean raiting
    pred_line <- sum_ordinal(pred_line)
    
    # Combine with predictors
    pred_line <- cbind(plot_dat_line, pred_line)
    
    # Prepare variables
    pred_line[, block := factor(block,
                                levels = block_levels,
                                labels = block_labels)]
    pred_line[, x := get(col)]
    
    # Predict for participants ----
    print("Computing raws means")

    # Bin and summarize
    rm <- as.data.table(model$data)
    rm <- rm[, .(m = mean(get(resp)),
                 sd = sd(get(resp)),
                 prec = 1 / sd(get(resp))), by = c("PID", "block", col)]
    rm[, bin_n := factor(dplyr::ntile(get(col), nbins))]
    rm[, bin := mean(get(col)), by = bin_n]
    rm <- rm[prec < Inf]
    rm_sum <-
      rm[, .(m = Hmisc::wtd.mean(m, weights = prec, normwt = T),
                  se = sqrt(Hmisc::wtd.var(
                    m, weights = prec, normwt = T
                  )
                  / .N)),
              by = c("bin", "block")]
    rm_sum[, block := factor(block,
                             levels = block_levels,
                             labels = block_labels)]
    
    print("Plotting")
    p <- ggplot(pred_line, aes(
      x = x,
      y = m,
      fill = block,
      color = block
    )) +
      labs(
        x = label,
        y = resp_label,
        color = "Block",
        fill = "Block",
        linetype = "Block"
      ) +
      scale_x_continuous(expand = expansion(mult = c(0, 0))) +
      scale_fill_manual(breaks = block_labels,
                        values = block_colors) +
      scale_color_manual(breaks = block_labels,
                         values = block_colors) +
      scale_linetype_manual(breaks = block_labels,
                            values = block_lines) +
      theme(legend.position = "none") +
      geom_pointrange(
        data = rm_sum,
        aes(
          x = bin,
          y = m,
          ymin = m - se,
          ymax = m + se,
          color = block
        ),
        alpha = 0.3,
        show.legend = F
      )
    
    p <- getGeoms(p,
                  pred_line,
                  col = "block",
                  fill_legend = T)
    
    # This might help with memory usage
    gc()
    
    return(p)
    
  }
  
  p_affect <- plot_pred("affect",
                        "Expected answer affect")
  
  p_confidence <- plot_pred("confidence",
                            "Confidence")
  
  p_useful <- plot_pred("useful",
                        "Expected ansewr usefulness")
  
  return(list(p_useful, p_confidence, p_affect))
}

plot_rating_grid <- function(...){
  
  plots_list <- list(...)
    
  l <- get_legend(plots_list[[1]] + theme(
      legend.position = "top",
      legend.justification = "center"
  ))
  
  p <- plot_grid(
    l,
    plot_grid(
      plotlist = plots_list,
      nrow = 1
    ),
    ncol = 1,
    rel_heights = c(.1, 1)
  )
  
  return(p)
}

plot_rating_ID_by_q <- function(model,
                                col,
                                label,
                                resp,
                                resp_label,
                                measures = c("coup_relevance_s",
                                             "coup_attitude_s",
                                             "affect_s",
                                             "motivation_s"),
                                quadratic = c("coup_attitude_s")) {
  
  # Prepare values for group mean prediction ----
  plot_dat <- as.data.table(
    expand.grid(
      col = plot_seq(model$data[col]),
      questionId = unique(model$data$questionId)
    )
  )
  
  colnames(plot_dat) <- c(col, "questionId")
  
  plot_dat <- merge(plot_dat, 
                    unique(as.data.table(model$data)[, .(questionId, block)]))
  

  # Set all additional predictors to median
  other_measures <- measures[measures != col]
  plot_dat[, (other_measures) := lapply(other_measures, function(x)
    median(model$data[x][[1]]))]
  
  # Compute quadratics
  if (!is.null(quadratic)) {
    lapply(quadratic, function(x) {
      plot_dat[, paste0("I(", x, ")^2") := .(get(x) ^ 2)]
    })
  }
  
  # Predict - this returns ndraws x npoints x 5
  pred_line <- fitted(
    model,
    newdata = plot_dat,
    re_formula = as.formula(paste0("~ (1 + ", col, " | questionId)")),
    summary = F,
    resp = resp,
    draw_ids = sample(1:4000, n_draws)
  )
    
  # Summarize into mean raiting
  pred_line <- sum_ordinal(pred_line)
  
  # Combine with predictors
  pred_line <- cbind(plot_dat, pred_line)
    
  # Prepare variables
  pred_line[, x := get(col)]
  
  # Add question text
  pred_line <- merge(pred_line, quest_text, by = "questionId", all.x = T)
  
  # Block labels
  pred_line[, block := factor(block,
                              levels = block_levels,
                              labels = block_labels)]
    
  d <- highlight_key(pred_line, ~questionId)
    
  p <- ggplot(d, aes(
    x = x,
    y = m,
    group = questionId,
    text = question,
    color = block
  )) +
    geom_line(linewidth = 0.3) +
    facet_wrap("block") +
    labs(
      x = label,
      y = resp_label,
    ) +
    scale_x_continuous(expand = expansion(mult = c(0, 0))) +
    scale_color_manual(breaks = block_labels,
                         values = block_colors) +
      scale_linetype_manual(breaks = block_labels,
                            values = block_lines) +
    theme(legend.position = "none")
  
  p <- ggplotly(p,
                tooltip = "text") %>%
    highlight(on = "plotly_hover", off = "plotly_deselect")

  # This might help with memory usage
  gc()
  
  return(p)
}

rmm1 <- brm(file = file.path(savedModelsDir, rating_model))

sampleName <- "v1.01"
source("load_data_and_exclude.R")
list[wait, rating_clps, know_test,
     prob_judge, quest, quality] = load_exclude(sampleName)

quest_text <- unique(wait[, .(questionId, question)])
quest_text[, question := trimws(question)]
quest_text <- unique(quest_text[, .(questionId, question)])
quest_text[, question := gsub('""""', '"', question)]

set.seed(0)
```

```{r ID_rating_plotting, message=FALSE, warning=FALSE, include=FALSE}
# Make plots
list[p_coup_rel_useful, 
     p_coup_rel_confidence, 
     p_coup_rel_affect] <- plot_rating_ID(rmm1, "coup_relevance_s", 
                                          "Coup relevance (std.)")
list[p_coup_att_useful, 
     p_coup_att_confidence, 
     p_coup_att_affect] <- plot_rating_ID(rmm1, "coup_attitude_s", 
                                          "Coup attitude (std.)")

list[p_aff_useful, 
     p_aff_confidence, 
     p_aff_affect] <- plot_rating_ID(rmm1, "affect_s", "Mood (std.)")

list[p_mot_useful, 
     p_mot_confidence, 
     p_mot_affect] <- plot_rating_ID(rmm1, "motivation_s", 
                                          "Motivational activation\n(std.)")

# Set common y limits
list[p_coup_rel_useful,
     p_coup_att_useful,
     p_aff_useful,
     p_mot_useful] <-
  set_common_y_limits(p_coup_rel_useful,
                      p_coup_att_useful,
                      p_aff_useful,
                      p_mot_useful)

list[p_coup_rel_confidence,
     p_coup_att_confidence,
     p_aff_confidence,
     p_mot_confidence] <-
  set_common_y_limits(p_coup_rel_confidence,
                      p_coup_att_confidence,
                      p_aff_confidence,
                      p_mot_confidence)

list[p_coup_rel_affect,
     p_coup_att_affect,
     p_aff_affect,
     p_mot_affect] <-
  set_common_y_limits(p_coup_rel_affect,
                      p_coup_att_affect,
                      p_aff_affect,
                      p_mot_affect)
```

## Model
The first part of this presentation contains plots with the outcome of a model predicting the three question rating measures. It uses a multivariate ordinal regression model. This is the formula for the model:


mv(useful, confidence, affect) ~ `r as.character(rmm1$formula[[1]]$confidence[[1]])[[3]]`

## Average ratings by coup relevance
```{r coup_relevance}
plot_rating_grid(p_coup_rel_useful,
                 p_coup_rel_confidence,
                 p_coup_rel_affect)
```

Lines are predictions from model, points denote raw means+-SE.

## Average ratings by coup attitude
```{r coup_attitude}
plot_rating_grid(p_coup_att_useful, 
     p_coup_att_confidence, 
     p_coup_att_affect
)
```

Lines are predictions from model, points denote raw means+-SE.
Seems like the polynomial does a decent job of capturing the shape here.


## Average ratings by mood
(STAI + Gallup wellbeing)

```{r affect}
plot_rating_grid(p_aff_useful,
                 p_aff_confidence,
                 p_aff_affect)
```

Lines are predictions from model, points denote raw means+-SE.


## Average ratings by motivaitonal activation
(Apathy questionnaire + Regulatory Mode)

```{r motivation}
plot_rating_grid(p_mot_useful,
                 p_mot_confidence,
                 p_mot_affect)
```

Lines are predictions from model, points denote raw means+-SE.

### Coup attitude changes the content deemed useful

```{r coup_rel_by_q}
plot_rating_ID_by_q(rmm1,
                    "coup_attitude_s",
                    "Coup attitude (std.)",
                    "useful",
                    "Expected usefulness")
```

Each line is a question. Hover over the line to read the question text.

### Confidence about the different answers changes with coup attitude

```{r coup_rel_by_q}
plot_rating_ID_by_q(rmm1,
                    "coup_attitude_s",
                    "Coup attitude (std.)",
                    "confidence",
                    "Confidence")
```

Each line is a question. Hover over the line to read the question text.

### Coup attitude changes the expected affective response to each answer

```{r coup_rel_by_q}
plot_rating_ID_by_q(rmm1,
                    "coup_attitude_s",
                    "Coup attitude (std.)",
                    "affect",
                    "Expected affect")
```

Each line is a question. Hover over the line to read the question text.