---
title: "Question attributes"
output: ioslides_presentation
date: "2024-02-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
# Load libraries
library(data.table)
setDTthreads(11)
library(ggplot2)
library(stringr)
library(cowplot)
library(testit)
theme_set(theme_minimal()  +
            theme_cowplot(14, font_family = "Helvetica", rel_small = 0.8) + 
            theme(legend.position = "none",
                  strip.text = element_text(size = 9),
                  plot.margin = margin(1.5,2,1.5,2)))
library(brms)
library(gsubfn)
library(plotly)
source("utils.R")


savedModelsDir <- file.path("..", "saved_models")
cacheDir <- file.path("..", "saved_models", "question_attributes")
res <- 100 # Plotting resolution for lines
n_draws <- 300 # Subset of draws for prediction
use_model <- "chm1"

# Colors, lines labels
block_colors <- c("#cc1337", "#005b8d")
block_labels <- c("Coup-related", "General")
block_levels <- c("coup", "general")
block_lines <- c("solid", "dashed")

plot_wait_know_attr <- function(model,
                                col,
                                label,
                                attributes = c("useful", "confidence", "affect"),
                                quadratic = T) {
  # Prepare values for prediction
  plot_dat <- rbindlist(lapply(unique(model$data$block),
                               function(x)
                                 data.table(col = plot_seq(model$data[col][model$data$block == x, ]),
                                            block = x)))
  
  colnames(plot_dat) <- c(col, "block")
  
  # Set all additional predictors to median
  plot_dat[, wait_s := 0]
  
  other_attr <- attributes[attributes != col]
  plot_dat[, (other_attr) := lapply(other_attr, function(x)
    median(model$data[x][[1]]))]
  
  if (quadratic) {
    plot_dat[, `I(confidence^2)` := confidence ^ 2]
    plot_dat[, `I(affect^2)` := affect ^ 2]
    plot_dat[, `I(useful^2)` := useful ^ 2]
  }
  
  # Predict - this returns ndraws x npoints x 3
  # Fit only if not saved
  pred_file <- file.path(cacheDir,
                         paste0(use_model,
                                "_",
                                col,
                                "_line_predictions.rda"))
  if (!file.exists(pred_file)) {
    pred <- fitted(
      model,
      newdata = plot_dat,
      re_formula = NA,
      summary = F,
      draw_ids = sample(1:4000, n_draws)
    )
    save(pred, file = pred_file)
  } else {
    load(pred_file)
  }
  
  
  # Summarize as wait, know vs. skip
  list[pred_wait, pred_know] <- sum_cat(pred)
  
  pred_wait <- cbind(plot_dat, pred_wait)
  
  # Predict per question
  qcoefs_data <- unique(as.data.table(model$data)[, .(questionId,
                                                      block,
                                                      confidence,
                                                      useful,
                                                      affect)], by = "questionId")
  # Take residuals over other attributres
  qcoefs_data[, (other_attr) := lapply(other_attr, function(x)
    median(model$data[x][[1]]))]
  qcoefs_data[, wait_s := 0]
  
  if (quadratic) {
    qcoefs_data[, `I(confidence^2)` := confidence ^ 2]
    qcoefs_data[, `I(affect^2)` := affect ^ 2]
    qcoefs_data[, `I(useful^2)` := useful ^ 2]
  }
  
  # Fit only if not saved
  qcoef_file <- file.path(cacheDir,
                         paste0(use_model,
                                "_",
                                col,
                                "_point_predictions.rda"))
  if (!file.exists(qcoef_file)) {
    qcoefs <- fitted(
      model,
      newdata = qcoefs_data,
      re_formula = ~ (1 + wait_s | questionId),
      summary = F,
      draw_ids = sample(1:4000, n_draws)
    )
    save(qcoefs, file = qcoef_file)
  } else {
    load(qcoef_file)
  }
  
  # Summarize as wait, know vs. skip
  list[qcoefs_wait, qcoefs_know] <- sum_cat(qcoefs)
  
  qcoefs_wait <- cbind(qcoefs_data, qcoefs_wait)
  qcoefs_know <- cbind(qcoefs_data, qcoefs_know)
  
  qcoefs_wait <- merge(qcoefs_wait, quest_text, by = "questionId")
  qcoefs_know <- merge(qcoefs_know, quest_text, by = "questionId")
  
  
  
  # Plot waiting
  pred_wait[, block := factor(block,
                              levels = block_levels,
                              labels = block_labels)]
  qcoefs_wait[, block := factor(block,
                                levels = block_levels,
                                labels = block_labels)]
  pred_wait[, x := get(col)]
  qcoefs_wait[, x := get(col)]
  
  p_wait <- ggplot(pred_wait, aes(
    x = x,
    y = m,
    fill = block,
    color = block
  )) +
    labs(
      x = label,
      y = "Prop. waited vs. skipped",
      color = "Block",
      fill = "",
      linetype = "Block"
    ) +
    scale_x_continuous(expand = expansion(mult = c(0, 0))) +
    scale_fill_manual(breaks = block_labels,
                      values = block_colors) +
    scale_color_manual(breaks = block_labels,
                       values = block_colors) +
    scale_linetype_manual(breaks = block_labels,
                          values = block_lines) +
    theme(legend.position = "none")
  
  p_wait <- p_wait + geom_point(data = qcoefs_wait,
                                aes(x = x,
                                    y = m,
                                    text = question),
                                alpha = 0.3)
  
  p_wait <- getGeoms(p_wait,
                     pred_wait,
                     col = "block",
                     fill_legend = T)
  
  
  # Plot know
  pred_know <- cbind(plot_dat, pred_know)
  pred_know[, block := factor(block,
                              levels = block_levels,
                              labels = block_labels)]
  qcoefs_know[, block := factor(block,
                                levels = block_levels,
                                labels = block_labels)]
  
  pred_know[, x := get(col)]
  qcoefs_know[, x := get(col)]
  
  p_know <- ggplot(pred_know, aes(
    x = x,
    y = m,
    fill = block,
    color = block
  )) +
    labs(
      x = label,
      y = "Prop. known vs. skipped",
      color = "Question type",
      fill = "Question type",
      linetype = "Question type"
    ) +
    scale_x_continuous(expand = expansion(mult = c(0, 0))) +
    scale_fill_manual(breaks = block_labels,
                      values = block_colors) +
    scale_color_manual(breaks = block_labels,
                       values = block_colors) +
    scale_linetype_manual(breaks = block_labels,
                          values = block_lines) +
    theme(legend.position = "none")
  
  p_know <- p_know + geom_point(data = qcoefs_know,
                                aes(
                                  x = x,
                                  y = m,
                                  color = block,
                                  text = question
                                ),
                                alpha = 0.3)
  
  p_know <- getGeoms(p_know,
                     pred_know,
                     col = "block",
                     fill_legend = T)
  
  list[p_wait, p_know] <- set_common_y_limits(p_wait, p_know)
  
  l <- get_legend(p_know + theme(
    legend.position = "top",
    legend.justification = "center"
  ))
  
  p_know <- ggplotly(p_know, tooltip = "question")
  
  p_wait <- ggplotly(p_wait, tooltip = "question")
  
  # Remove legend from anything but lines
  for (ii in c(1:4, 6,7)) {
    p_know$x$data[[ii]]$showlegend <- F
    p_wait$x$data[[ii]]$showlegend <- F
  }
  p_know$x$data[[5]]$showlegend <- F
  p_know$x$data[[8]]$showlegend <- F
  
  p <- subplot(p_wait,
               p_know,
               titleX = T,
               titleY = T,
               margin = 0.05) %>%
    layout(
      showlegend = T,
      legend = list(
        x = 0,
        xanchor = 'left',
        yanchor = 'top'
      )
    )
  
  # This might help with memory usage
  gc()
  
  return(p)
}

chm1 <- brm(file = file.path(savedModelsDir, use_model))

sampleName <- "v1.01"
source("load_data_and_exclude.R")
list[wait, rating_clps, know_test,
     prob_judge, quest, quality] = load_exclude(sampleName)

quest_text <- unique(wait[, .(questionId, question)])
quest_text[, question := gsub('""""', '"', question)]

set.seed(0)
```

## Model
This presentation contains plots with the outcome of a model predicting choosing 'wait' and choosing 'know', relative to choosing 'skip'. It uses a categorical model, and the effects on wait and know can be thought of as independent. This is the formula for the model:

`r as.character(chm1$formula)[[1]]`

## Perceived answer usefulness
```{r usefulness}
plot_wait_know_attr(chm1, "useful", "Percieved answer usefulness (std.)")
```
Points are adjusted for other attributes (confidence, affect), and so don't align across slides.

## Confidence about answer
```{r confidence}
plot_wait_know_attr(chm1, "confidence", "Confidence about answer (std.)")
```
Points are adjusted for other attributes (confidence, affect), and so don't align across slides.


## Excpected affective response to answer
```{r affect}
plot_wait_know_attr(chm1, "affect", "Expected affective response (std.)\n(negative to positive)")
```
Points are adjusted for other attributes (confidence, affect), and so don't align across slides.

## Wait duration
```{r duration}
# Prepare values for prediction
plot_dat <- as.data.table(
  expand.grid(
    wait_s = unique(chm1$data$wait_s),
    block = NA,
    confidence = median(chm1$data$confidence),
    useful = median(chm1$data$useful),
    affect = median(chm1$data$affect)
  )
)

plot_dat[, `I(confidence^2)` := confidence ^ 2]
plot_dat[, `I(affect^2)` := affect ^ 2]
plot_dat[, `I(useful^2)` := useful ^ 2]

# Predict - this returns ndraws x npoints x 3
pred_file <- file.path(cacheDir,
                       paste0(use_model,
                              "_duration_line_predictions.rda"))
if (!file.exists(pred_file)) {

  pred <- fitted(
    chm1,
    newdata = plot_dat,
    re_formula = NA,
    summary = F,
    draw_ids = sample(1:4000, n_draws)
  )
  save(pred, file = pred_file)
} else {
  load(pred_file)
}

# Summarize as wait, know vs. skip
list[pred_wait, pred_know] <- sum_cat(pred)

# Plot waiting
pred_wait <- cbind(plot_dat, pred_wait)

pred_wait[, dur := c(3,6,9,12)]

p_dur_wait <- ggplot(pred_wait, aes(
  x = dur,
  y = m,
  ymin = lb,
  ymax = ub,
)) +
  geom_pointrange() +
  labs(
    x = "Wait duration (s)",
    y = "Prop. waited vs. skipped",
  )

# Plot know
pred_know <- cbind(plot_dat, pred_know)
pred_know[, block := factor(block,
                            levels = block_levels,
                            labels = block_labels)]
pred_know[, dur := c(3,6,9,12)]

p_dur_know <- ggplot(pred_know, aes(
  x = dur,
  y = m,
  ymin = lb,
  ymax = ub,
)) +
  geom_pointrange() +
  labs(
    x = "Wait duration (s)",
    y = "Prop. known vs. skipped",
  )

list[p_dur_wait, p_dur_know] <- set_common_y_limits(p_dur_wait, p_dur_know)

plot_grid(p_dur_wait,
            p_dur_know,
            nrow = 1)
```

## Relations between question attributes

```{r attr_cor}
# Free up memory
rm(chm1)

rm0 <- brm(file = file.path(savedModelsDir, "rm0"))

qatr_plot_data <- unique(as.data.table(rm0$data)[, .(block, questionId)])

qatr_file <- file.path(cacheDir,
                       paste0("rm0_question_predictions.rda"))
if (!file.exists(qatr_file)) {
  qatr_fitted_mat <- fitted(rm0,
                        newdata = qatr_plot_data,
                        re_formula = "mvbind(confidence, affect, useful) ~ 1 + block + (1 | q | questionId)",
                        scale = "linear",
                        probs = c(0.25, 0.75))
  save(qatr_fitted_mat, file = qatr_file)
}else{
  load(qatr_file)
}

rownames(qatr_fitted_mat) <- qatr_plot_data$questionId

# Convert to data.table
qatr_fitted <- as.data.table(qatr_fitted_mat)

# Add prefix to column names based on third dimension
qatr_fitted[, variable := paste(V3, V2, sep = "_")]

# Convert back to wide format
qatr_fitted <- dcast(qatr_fitted[, .(V1, value, variable)], V1 ~ variable, 
                     value.var = "value")

colnames(qatr_fitted)[1] <- "questionId"

qatr_fitted <- merge(qatr_fitted, qatr_plot_data, by = "questionId", all.x = T)
qatr_fitted[, block := factor(block,
                              levels = block_levels,
                              labels = block_labels)]

qatr_fitted <- merge(qatr_fitted, quest_text, by = "questionId")

p_conf_use <- ggplot(qatr_fitted, aes(x = confidence_Estimate, 
                                      y = useful_Estimate, 
                                      color = block)) +
  geom_errorbarh(aes(xmin = confidence_Q25, xmax = confidence_Q75)) +
  geom_errorbar(aes(ymin = useful_Q25, ymax = useful_Q75)) +
  geom_point(aes(text = question)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE) +
  labs(x = "Confidence (std.)",
       y = "Usefulness (std.)") +
  scale_color_manual(breaks = block_labels,
                       values = block_colors)

p_conf_aff <- ggplot(qatr_fitted, aes(x = confidence_Estimate, 
                                      y = affect_Estimate, 
                                      color = block)) +
  geom_errorbarh(aes(xmin = confidence_Q25, xmax = confidence_Q75)) +
  geom_errorbar(aes(ymin = affect_Q25, ymax = affect_Q75)) +
  geom_point(aes(text = question)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE) +
  labs(x = "Confidence (std.)",
       y = "Expected affect (std.)") +
  scale_color_manual(breaks = block_labels,
                       values = block_colors)

p_use_aff <- ggplot(qatr_fitted, aes(x = affect_Estimate, 
                                     y = useful_Estimate, 
                                     color = block)) +
  geom_errorbar(aes(ymin = useful_Q25, ymax = useful_Q75)) +
  geom_errorbarh(aes(xmin = affect_Q25, xmax = affect_Q75)) +
  geom_point(aes(text = question)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE) +
  labs(y = "Usefulness (std.)",
       x = "Expected affect (std.)",
       color = "Question type") +
  scale_color_manual(breaks = block_labels,
                       values = block_colors)

# attr_l <- get_legend(p_use_aff + theme(legend.position = "top",
#     legend.justification = "center"))

# plot_grid(
#   attr_l,
#   plot_grid(
#     p_conf_use,
#     p_conf_aff,
#     p_use_aff,
#     nrow = 1
#   ),
#   ncol = 1,
#   rel_heights = c(.1, 1)
# )

p_conf_use <- ggplotly(p_conf_use, tooltip = "text")
p_conf_aff <- ggplotly(p_conf_aff, tooltip = "text")
p_use_aff <- ggplotly(p_use_aff, tooltip = "text")

subplot(
  p_conf_use,
  p_conf_aff,
  p_use_aff,
  titleX = T,
  titleY = T,
  margin = 0.05
) %>% layout()
```
Polynomial regression lines for plotting purposes only.

