---
title: "Question attributes"
output: ioslides_presentation
date: "2024-02-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
# Load libraries
library(data.table)
setDTthreads(11)
library(ggplot2)
library(stringr)
library(cowplot)
library(testit)
theme_set(theme_minimal()  +
            theme_cowplot(14, font_family = "Helvetica", rel_small = 0.8) + 
            theme(legend.position = "none",
                  strip.text = element_text(size = 9),
                  plot.margin = margin(1.5,2,1.5,2)))
library(brms)
library(gsubfn)
source("utils.R")


savedModelsDir <- file.path("..", "saved_models")
res <- 100 # Plotting resolution for lines
n_draws <- 300 # Subset of draws for prediction

# Colors, lines labels
block_colors <- c("#cc1337", "#005b8d")
block_labels <- c("Coup-related", "General")
block_levels <- c("coup", "general")
block_lines <- c("solid", "dashed")


# Return sequence for plotting
plot_seq <- function(x){
  return(seq(min(x), max(x), length.out = res))
}

# Summarize draws from categorical model
llb <- function(x) quantile(x, 0.025)
lb <- function(x) quantile(x, 0.25)
ub <- function(x) quantile(x, 0.75)
uub <- function(x) quantile(x, 0.975)
sum_draws <- function(x) data.table(
  m = apply(x, 2, median),
  llb = apply(x, 2, llb),
  lb = apply(x, 2, lb),
  ub = apply(x, 2, ub),
  uub = apply(x, 2, uub)
)

sum_cat <- function(pred){
  assert("Skip, wait, know not in the expected order", 
         sum(names(pred[1,1,]) == c("skip", "wait", "know")) == 3)
  
  # Calculate wait vs. skip
  pred_wait <- pred[, , 2] / (pred[, , 1] + pred[, , 2])
  
  assert("operation wasn't elementwise",
         pred_wait[1,1] == (pred[1, 1, 2] / (pred[1, 1, 1] + pred[1, 1, 2])))
  
  # Summarize over draws
  pred_wait <- sum_draws(pred_wait)
  
  # Calculate know vs. skip
  pred_know <- pred[, , 3] / (pred[, , 1] + pred[, , 3])
  
  # Summarize over draws
  pred_know <- sum_draws(pred_know)
  
  return(list(pred_wait, pred_know))
}

plot_wait_know_attr <- function(model, col, label,
                                attributes = c("useful", "confidence", "affect"),
                                quadratic = T) {
  
  # Prepare values for prediction
  plot_dat <- rbindlist(lapply(unique(model$data$block), 
                     function(x) data.table(
                       col = plot_seq(model$data[col][model$data$block == x,]),
                       block = x)))
    
  colnames(plot_dat) <- c(col, "block")
  
  # Set all additional predictors to median
  plot_dat[, wait_s := median(model$data$wait_s)]
  
  other_attr <- attributes[attributes != col]
  plot_dat[, (other_attr) := lapply(other_attr, function(x)
    median(model$data[x][[1]]))]
  
  if (quadratic){
    plot_dat[, `I(confidence^2)` := confidence ^ 2]
    plot_dat[, `I(affect^2)` := affect ^ 2]
    plot_dat[, `I(useful^2)` := useful ^ 2]
  }
  
  # Predict - this returns ndraws x npoints x 3
  pred <- fitted(
    model,
    newdata = plot_dat,
    re_formula = NA,
    summary = F,
    draw_ids = sample(1:4000, n_draws)
  )
  
  # Summarize as wait, know vs. skip
  list[pred_wait, pred_know] <- sum_cat(pred)
  
  # Plot waiting
  pred_wait <- cbind(plot_dat, pred_wait)
  pred_wait[, block := factor(block,
                              levels = block_levels,
                              labels = block_labels)]
  pred_wait[, x := get(col)]
  
  p_wait <- ggplot(pred_wait, aes(
    x = x,
    y = m,
    fill = block,
    color = block
  )) +
    labs(
      x = label,
      y = "Prop. waited vs. skipped",
      color = "Block",
      fill = "",
      linetype = "Block"
    ) +
    scale_x_continuous(expand = expansion(mult = c(0, 0))) +
    scale_fill_manual(breaks = block_labels,
                      values = block_colors) +
    scale_color_manual(breaks = block_labels,
                       values = block_colors) +
    scale_linetype_manual(breaks = block_labels,
                          values = block_lines) +
    theme(legend.position = "none")
  
  p_wait <- getGeoms(p_wait,
                     pred_wait,
                     col = "block",
                     fill_legend = T)
  
  # Plot know
  pred_know <- cbind(plot_dat, pred_know)
  pred_know[, block := factor(block,
                              levels = block_levels,
                              labels = block_labels)]
  pred_know[, x := get(col)]
  
  p_know <- ggplot(pred_know, aes(
    x = x,
    y = m,
    fill = block,
    color = block
  )) +
    labs(
      x = label,
      y = "Prop. known vs. skipped",
      color = "Question type",
      fill = "Question type",
      linetype = "Question type"
    ) +
    scale_x_continuous(expand = expansion(mult = c(0, 0))) +
    scale_fill_manual(breaks = block_labels,
                      values = block_colors) +
    scale_color_manual(breaks = block_labels,
                       values = block_colors) +
    scale_linetype_manual(breaks = block_labels,
                          values = block_lines) +
    theme(legend.position = "none")
  
  p_know <- getGeoms(p_know,
                     pred_know,
                     col = "block",
                     fill_legend = T)
  
  list[p_wait, p_know] <- set_common_y_limits(p_wait, p_know)
  
  l <- get_legend(p_know + theme(
    legend.position = "top",
    legend.justification = "center"
  ))
  
  p <- plot_grid(
    l,
    plot_grid(p_wait,
              p_know,
              nrow = 1),
    rel_heights = c(.1, 1),
    ncol = 1
  )
  
  # This might help with memory usage
  gc()
  
  return(p)
}

chm1 <- brm(file = file.path(savedModelsDir, "chm1"))

set.seed(0)
```

## Model
This presentation contains plots with the outcome of a model predicting choosing 'wait' and choosing 'know', relative to choosing 'skip'. It uses a categorical model, and the effects on wait and know can be thought of as independent. This is the formula for the model:

`r as.character(chm1$formula)[[1]]`

## Perceived answer usefulness
```{r usefulness}
plot_wait_know_attr(chm1, "useful", "Percieved answer usefulness (std.)")
```

## Confidence about answer
```{r confidence}
plot_wait_know_attr(chm1, "confidence", "Confidence about answer (std.)")
```


## Excpected affective response to answer
```{r affect}
plot_wait_know_attr(chm1, "affect", "Expected affective response (std.)\n(negative to positive)")
```

## Wait duration
```{r duration}
# Prepare values for prediction
plot_dat <- as.data.table(
  expand.grid(
    wait_s = unique(chm1$data$wait_s),
    block = NA,
    confidence = median(chm1$data$confidence),
    useful = median(chm1$data$useful),
    affect = median(chm1$data$affect)
  )
)

plot_dat[, `I(confidence^2)` := confidence ^ 2]
plot_dat[, `I(affect^2)` := affect ^ 2]
plot_dat[, `I(useful^2)` := useful ^ 2]

# Predict - this returns ndraws x npoints x 3
pred <- fitted(
  chm1,
  newdata = plot_dat,
  re_formula = NA,
  summary = F,
  draw_ids = sample(1:4000, n_draws)
)

# Summarize as wait, know vs. skip
list[pred_wait, pred_know] <- sum_cat(pred)

# Plot waiting
pred_wait <- cbind(plot_dat, pred_wait)

pred_wait[, dur := c(3,6,9,12)]

p_dur_wait <- ggplot(pred_wait, aes(
  x = dur,
  y = m,
  ymin = lb,
  ymax = ub,
)) +
  geom_pointrange() +
  labs(
    x = "Wait duration (s)",
    y = "Prop. waited vs. skipped",
  )

# Plot know
pred_know <- cbind(plot_dat, pred_know)
pred_know[, block := factor(block,
                            levels = block_levels,
                            labels = block_labels)]
pred_know[, dur := c(3,6,9,12)]

p_dur_know <- ggplot(pred_know, aes(
  x = dur,
  y = m,
  ymin = lb,
  ymax = ub,
)) +
  geom_pointrange() +
  labs(
    x = "Wait duration (s)",
    y = "Prop. known vs. skipped",
  )

list[p_dur_wait, p_dur_know] <- set_common_y_limits(p_dur_wait, p_dur_know)

plot_grid(p_dur_wait,
            p_dur_know,
            nrow = 1)
```

## Relations between question attributes

```{r attr_cor}
# Free up memory
rm(chm1)

rm0 <- brm(file = file.path(savedModelsDir, "rm0"))

qatr_plot_data <- unique(as.data.table(rm0$data)[, .(block, questionId)])

qatr_fitted_mat <- fitted(rm0,
                      newdata = qatr_plot_data,
                      re_formula = "mvbind(confidence, affect, useful) ~ 1 + block + (1 | q | questionId)",
                      scale = "linear",
                      probs = c(0.25, 0.75))

rownames(qatr_fitted_mat) <- qatr_plot_data$questionId

# Convert to data.table
qatr_fitted <- as.data.table(qatr_fitted_mat)

# Add prefix to column names based on third dimension
qatr_fitted[, variable := paste(V3, V2, sep = "_")]

# Convert back to wide format
qatr_fitted <- dcast(qatr_fitted[, .(V1, value, variable)], V1 ~ variable, 
                     value.var = "value")

colnames(qatr_fitted)[1] <- "questionId"

qatr_fitted <- merge(qatr_fitted, qatr_plot_data, by = "questionId", all.x = T)
qatr_fitted[, block := factor(block,
                              levels = block_levels,
                              labels = block_labels)]

p_conf_use <- ggplot(qatr_fitted, aes(x = confidence_Estimate, y = useful_Estimate, color = block)) +
  geom_errorbarh(aes(xmin = confidence_Q25, xmax = confidence_Q75)) +
  geom_errorbar(aes(ymin = useful_Q25, ymax = useful_Q75)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE) +
  labs(x = "Confidence (std.)",
       y = "Usefulness (std.)") +
  scale_color_manual(breaks = block_labels,
                       values = block_colors)

p_conf_aff <- ggplot(qatr_fitted, aes(x = confidence_Estimate, y = affect_Estimate, color = block)) +
  geom_errorbarh(aes(xmin = confidence_Q25, xmax = confidence_Q75)) +
  geom_errorbar(aes(ymin = affect_Q25, ymax = affect_Q75)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE) +
  labs(x = "Confidence (std.)",
       y = "Expected affect (std.)") +
  scale_color_manual(breaks = block_labels,
                       values = block_colors)

p_use_aff <- ggplot(qatr_fitted, aes(x = affect_Estimate, y = useful_Estimate, color = block)) +
  geom_errorbar(aes(ymin = useful_Q25, ymax = useful_Q75)) +
  geom_errorbarh(aes(xmin = affect_Q25, xmax = affect_Q75)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE) +
  labs(y = "Usefulness (std.)",
       x = "Expected affect (std.)",
       color = "Question type") +
  scale_color_manual(breaks = block_labels,
                       values = block_colors)

attr_l <- get_legend(p_use_aff + theme(legend.position = "top",
    legend.justification = "center"))

plot_grid(
  attr_l,
  plot_grid(
    p_conf_use,
    p_conf_aff,
    p_use_aff,
    nrow = 1
  ),
  ncol = 1,
  rel_heights = c(.1, 1)
)
```
Polynomial regression lines for plotting purposes only.

